\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[margin=0.5in]{geometry} % Sets smaller margins
\title{Lab 05: Beer's Law and Molecular Spectroscopy}


\begin{document}


\section*{Safety Measures}
\begin{itemize}
    \item Copper (II) sulfate (CuSO$_4$) is toxic and harmful to the environment; handle with care and dispose of waste in designated containers.
    \item Avoid skin contact with CuSO$_4$ as it is a skin irritant. Rinse thoroughly with water if contact occurs.
    \item Always wear lab-appropriate PPE, including gloves, goggles, and a lab coat.
\end{itemize}

\section*{Materials}
\begin{itemize}
    \item Spectrophotometer (Spectronic 200)
    \item Cuvettes (1 cm), Pipettes, Beakers, Magnetic stir plate and stir bar
    \item Volumetric flasks (100 mL), DI water, Solid CuSO$_4$·5H$_2$O
\end{itemize}

\section*{Procedure}

\subsection*{Spectrophotometer Setup}
\begin{enumerate}
    \item Turn on the spectrophotometer and initialize it.
    \item Set to "Absorbance" mode at $\lambda = 600$ nm.
    \item Zero the device using a DI water blank.
\end{enumerate}

\subsection*{Preparation of Calibration Solutions}
\begin{enumerate}
    \item Prepare CuSO$_4$ solutions in concentrations from 0.1 M to 0.5 M.
    \item For each solution:
    \begin{itemize}
        \item Weigh CuSO$_4$·5H$_2$O and dissolve in 50 mL of DI water in a beaker.
        \item Transfer to a 100 mL volumetric flask and dilute to the mark with DI water.
    \end{itemize}
\end{enumerate}

\subsection*{Creating the Calibration Curve}
\begin{enumerate}
    \item Measure the absorbance of each calibration solution using the spectrophotometer.
    \item Record data, and create a linear regression plot of absorbance vs. concentration.
\end{enumerate}

\subsection*{Determination of Unknown Concentration}
\begin{enumerate}
    \item Obtain an unknown CuSO$_4$ solution and measure its absorbance.
    \item Calculate its concentration using the calibration curve.
\end{enumerate}

\subsection*{Absorption Spectrum Measurement}
\begin{enumerate}
    \item Set the spectrophotometer to wavelengths between 500–700 nm, measuring absorbance at intervals of 20 nm.
\end{enumerate}

\section*{Cleanup}
\begin{itemize}
    \item Dispose of CuSO$_4$ solutions in the waste barrel.
    \item Wash all glassware and wipe down the lab bench.
\end{itemize}

\end{document}